---
title: "Ecosystem Modeling Project"
author: "Hannah Curtis"
date: "2023-04-26"
output: html_document
---
Reading Water Level Files:
```{r}
# base water level
basecase <- read.csv("basecase_WL.tsv", sep='\t', header=TRUE)
time <- basecase$Time..Hour.
base_WL <- basecase$Pond.Water.Level...Final

#min pond area
min_pond_area <- read.csv("min_area_WL.tsv", sep='\t', header=TRUE)
min_pa_WL <- min_pond_area$Pond.Water.Level...Final

#max pond area
max_pond_area <- read.csv("max_area_WL.tsv", sep='\t', header=TRUE)
max_pa_WL <- max_pond_area$Pond.Water.Level...Final

#min weir height
min_weir_height <- read.csv("min_weir_height_WL.tsv", sep='\t', header=TRUE)
min_wh_WL <- min_weir_height$Pond.Water.Level...Final

#max weir height
max_weir_height <- read.csv("max_weir_height_WL.tsv", sep='\t', header=TRUE)
max_wh_WL <- max_weir_height$Pond.Water.Level...Final

#min weir angle
min_weir_angle <- read.csv("min_weir_angle_WL.tsv", sep='\t', header=TRUE)
min_wa_WL <- min_weir_angle$Pond.Water.Level...Final

#max weir angle
max_weir_angle <- read.csv("max_weir_angle_WL.tsv", sep='\t', header=TRUE)
max_wa_WL <- max_weir_angle$Pond.Water.Level...Final

#min percent impervious
min_percent_imp <- read.csv("min_percent_imp_WL.tsv", sep='\t', header=TRUE)
min_pi_WL <- min_percent_imp$Pond.Water.Level...Final

#max percent impervious
max_percent_imp <- read.csv("max_percent_imp_WL.tsv", sep='\t', header=TRUE)
max_pi_WL <- max_percent_imp$Pond.Water.Level...Final

#min watershed area
min_watershed_area <- read.csv("min_watershed_area_WL.tsv", sep='\t', header=TRUE)
min_wata_WL <- min_watershed_area$Pond.Water.Level...Final

#max watershed area
max_watershed_area <- read.csv("max_watershed_area_WL.tsv", sep='\t', header=TRUE)
max_wata_WL <- max_watershed_area$Pond.Water.Level...Final

```

Reading Inflow/Outflow Files:
```{r}
# base inflow
basecase_i <- read.csv("base_inflow.tsv", sep='\t', header=TRUE)
time_hydrograph <- basecase_i$Time..Hour.
base_i <- basecase_i$Total.Inflow...Final

# base outflow
basecase_o <- read.csv("base_outflow.tsv", sep='\t', header=TRUE)
base_o <- basecase_o$Outflow...Final

# min pond area outflow
min_pond_area_o <- read.csv("min_area_outflow.tsv", sep='\t', header=TRUE)
min_pa_o <- min_pond_area_o$Outflow...Final

# max pond area outflow
max_pond_area_o <- read.csv("max_area_outflow.tsv", sep='\t', header=TRUE)
max_pa_o <- max_pond_area_o$Outflow...Final

# min weir angle outflow
min_weir_angle_o <- read.csv("min_weir_angle_outflow.tsv", sep='\t', header=TRUE)
min_wa_o <- min_weir_angle_o$Outflow...Final

# max weir angle outflow
max_weir_angle_o <- read.csv("max_weir_angle_outflow.tsv", sep='\t', header=TRUE)
max_wa_o <- max_weir_angle_o$Outflow...Final

# min watershed area inflow
min_ws_area_i <- read.csv("min_watershed_area_inflow.tsv", sep='\t', header=TRUE)
min_wata_i <- min_ws_area_i$Total.Inflow...Final

# max watershed area inflow
max_ws_area_i <- read.csv("max_watershed_area_inflow.tsv", sep='\t', header=TRUE)
max_wata_i <- max_ws_area_i$Total.Inflow...Final

# min watershed area outflow
min_ws_area_o <- read.csv("min_watershed_area_outflow.tsv", sep='\t', header=TRUE)
min_wata_o <- min_ws_area_o$Outflow...Final

# max watershed area outflow
max_ws_area_o <- read.csv("max_watershed_area_outflow.tsv", sep='\t', header=TRUE)
max_wata_o <- max_ws_area_o$Outflow...Final

# min percent impervious inflow
min_percent_imp_i <- read.csv("min_percent_imp_inflow.tsv", sep='\t', header=TRUE)
min_pi_i <- min_percent_imp_i$Total.Inflow...Final

# max percent impervious inflow
max_percent_imp_i <- read.csv("max_percent_imp_inflow.tsv", sep='\t', header=TRUE)
max_pi_i <- max_percent_imp_i$Total.Inflow...Final

# min percent impervious outflow
min_percent_imp_o <- read.csv("min_percent_imp_outflow.tsv", sep='\t', header=TRUE)
min_pi_o <- min_percent_imp_o$Outflow...Final

# max percent impervious outflow
max_percent_imp_o <- read.csv("max_percent_imp_outflow.tsv", sep='\t', header=TRUE)
max_pi_o <- max_percent_imp_o$Outflow...Final

```

Pond Area Plots
```{r}
plot(time,base_WL, type="l", col="blue", lwd=2, ylim=c(min(max_pa_WL),max(max_wata_WL)), xlab= "", ylab="")

lines(time, min_pa_WL, col="magenta", lwd=2)
lines(time, max_pa_WL, col="chartreuse3", lwd=2)

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Water Level (m)", line=2, cex.lab=1.5)

legend("topright",c("2,500", "5,625", "10,000"), 
       col=c("magenta", "blue", "chartreuse3"), 
       lty=c("solid", "solid", "solid"), title = "Pond Area (m2)")
```
Weir Height Plots: NOT USING
```{r }
plot(time,base_WL, type="l", col="blue", lwd=2, ylim=c(min(max_pa_WL),max(max_wata_WL)), xlab= "", ylab="")

lines(time, min_wh_WL, col="magenta", lwd=2)
lines(time, max_wh_WL, col="chartreuse3", lwd=2)

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Water Level (m)", line=2, cex.lab=1.5)

legend("topright",c("0.25", "0.5", "0.75"), 
       col=c("magenta", "blue", "chartreuse3"), 
        lty=c("solid", "solid", "solid"), title = "Height to Bottom of Weir (m)")
```
Weir Angle Plots
```{r }
plot(time,base_WL, type="l", col="blue", lwd=2, ylim=c(min(max_pa_WL),max(max_wata_WL)), xlab= "", ylab="")

lines(time, min_wa_WL, col="magenta", lwd=2)
lines(time, max_wa_WL, col="chartreuse3", lwd=2)

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Water Level (m)", line=2, cex.lab=1.5)

legend("topright",c("20", "60", "120"), 
       col=c("magenta", "blue", "chartreuse3"), 
        lty=c("solid", "solid", "solid"), title = "Weir Angle (degrees)")
```
Percent Impervious Area Plots
```{r }
plot(time,base_WL, type="l", col="blue", lwd=2, ylim=c(min(max_pa_WL),max(max_wata_WL)), xlab= "", ylab="")

lines(time, min_wata_WL, col="magenta", lwd=2)
lines(time, max_wata_WL, col="chartreuse3", lwd=2)

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Water Level (m)", line=2, cex.lab=1.5)

legend("topright",c("40,000", "100,000", "200,000"), 
       col=c("magenta", "blue", "chartreuse3"), 
        lty=c("solid", "solid", "solid"), title = "Watershed Area (m2)")
```
Watershed Area Plots
```{r }
plot(time,base_WL, type="l", col="blue", lwd=2, ylim=c(min(max_pa_WL),max(max_wata_WL)), xlab= "", ylab="")

lines(time, min_pi_WL, col="magenta", lwd=2)
lines(time, max_pi_WL, col="chartreuse3", lwd=2)

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Water Level (m)", line=2, cex.lab=1.5)

legend("topright",c("10", "25", "50"), 
       col=c("magenta", "blue", "chartreuse3"), 
        lty=c("solid", "solid", "solid"), title = "Percent Impervious (%)")
```
Base Storm Hydrograph
```{r }
plot(time_hydrograph, base_i, type="l", col="blue", lwd=2, xlab= "", ylab="")


lines(time_hydrograph, base_o, col="blue", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("blue", "blue"), 
       lty=c("solid", "dashed"))
```
Min Pond Area Storm Hydrograph
```{r }
plot(time_hydrograph, base_i, type="l", col="magenta", lwd=2, xlab= "", ylab="")

lines(time_hydrograph, min_pa_o, col="magenta", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("magenta", "magenta"), 
       lty=c("solid", "dashed"))
```
Max Pond Area Storm Hydrograph
```{r }
plot(time_hydrograph, base_i, type="l", col="chartreuse3", lwd=2, xlab= "", ylab="")

lines(time_hydrograph, max_pa_o, col="chartreuse3", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("chartreuse3", "chartreuse3"), 
       lty=c("solid", "dashed"))

```


Min Weir Angle Storm Hydrograph 
```{r }
plot(time_hydrograph, base_i, type="l", col="magenta", lwd=2, xlab= "", ylab="")

lines(time_hydrograph, min_wa_o, col="magenta", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("magenta", "magenta"), 
       lty=c("solid", "dashed"))

```

Max Weir Angle Storm Hydrograph 
```{r }
plot(time_hydrograph, base_i, type="l", col="chartreuse3", lwd=2, xlab= "", ylab="")

lines(time_hydrograph, max_wa_o, col="chartreuse3", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("chartreuse3", "chartreuse3"), 
       lty=c("solid", "dashed"))

```

Min Watershed Area Storm Hydrograph
```{r }
plot(time_hydrograph, min_wata_i, type="l", col="magenta", lwd=2, ylim=c(min(min_wata_i),max(max_wata_i)), xlab= "", ylab="")

lines(time_hydrograph, min_wata_o, col="magenta", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("magenta", "magenta"), 
       lty=c("solid", "dashed"))

```

Max Watershed Area Storm Hydrograph
```{r }
plot(time_hydrograph, max_wata_i, type="l", col="chartreuse3", lwd=2, xlab= "", ylab="")

lines(time_hydrograph, max_wata_o, col="chartreuse3", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("chartreuse3", "chartreuse3"), 
       lty=c("solid", "dashed"))

```

Min Percent Impervious Storm Hydrograph
```{r }
plot(time_hydrograph, min_pi_i, type="l", col="magenta", lwd=2, ylim=c(min(min_pi_i),max(base_i)), xlab= "", ylab="")

lines(time_hydrograph, min_pi_o, col="magenta", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("magenta", "magenta"), 
       lty=c("solid", "dashed"))

```

Max Percent Impervious Storm Hydrograph
```{r }
plot(time_hydrograph, max_pi_i, type="l", col="chartreuse3", lwd=2, xlab= "", ylab="")

lines(time_hydrograph, max_pi_o, col="chartreuse3", lwd=2, lty="dashed")

title(xlab="Time (hr)", line=2.5, cex.lab=1.5)
title(ylab="Flow (m3/hr)", line=2.5, cex.lab=1.5)

legend("topright",c("Inflow", "Outflow"), 
       col=c("chartreuse3", "chartreuse3"), 
       lty=c("solid", "dashed"))

```


40,000m2 watershed

Reading Water Level Files 25% impervious:
```{r}
# base water level
basecase_25 <- read.csv("test_percent_imp.tsv", sep='\t', header=TRUE)
base_25 <- basecase_25$Pond.Water.Level...Final
time_25 <- basecase_25$Time..Hour.

#min pond area
min_pond_area_25 <- read.csv("min_pond_area_25.tsv", sep='\t', header=TRUE)
min_pa_25 <- min_pond_area_25$Pond.Water.Level...Final

#max pond area
max_pond_area_25 <- read.csv("max_pond_area_25.tsv", sep='\t', header=TRUE)
max_pa_25 <- max_pond_area_25$Pond.Water.Level...Final

#min weir angle
min_weir_angle_25 <- read.csv("min_weir_angle_25.tsv", sep='\t', header=TRUE)
min_wa_25 <- min_weir_angle_25$Pond.Water.Level...Final

#max weir angle
max_weir_angle_25 <- read.csv("max_weir_angle_25.tsv", sep='\t', header=TRUE)
max_wa_25 <- max_weir_angle_25$Pond.Water.Level...Final

# min pond area min weir angle
min_pond_area_min_weir_angle_25 <- read.csv("min_area_angle_25.tsv", sep='\t', header=TRUE)
min_pa_min_wa_25 <- min_pond_area_min_weir_angle_25$Pond.Water.Level...Final

# min pond area max weir angle 
min_pond_area_max_weir_angle_25 <- read.csv("min_area_max_angle_25.tsv", sep='\t', header=TRUE)
min_pa_max_wa_25 <- min_pond_area_max_weir_angle_25$Pond.Water.Level...Final

# max pond area min weir angle 
max_pond_area_min_weir_angle_25 <- read.csv("max_area_min_angle_25.tsv", sep='\t', header=TRUE)
max_pa_min_wa_25 <- max_pond_area_min_weir_angle_25$Pond.Water.Level...Final

# max pond area max weir angle 
max_pond_area_max_weir_angle_25 <- read.csv("max_area_angle_25.tsv", sep='\t', header=TRUE)
max_pa_max_wa_25 <- max_pond_area_max_weir_angle_25$Pond.Water.Level...Final

```

Reading Inflow/Outflow Files 25% impervious:
```{r}
# base inflow
basecase_i_25 <- read.csv("base_inflow_25.tsv", sep='\t', header=TRUE)
time_hydrograph <- basecase_i_25$Time..Hour.
base_i_25 <- basecase_i_25$Total.Inflow...Final

# base outflow
basecase_o_25 <- read.csv("base_outflow_25.tsv", sep='\t', header=TRUE)
base_o_25 <- basecase_o_25$Outflow...Final

# min pond area outflow
min_pond_area_o_25 <- read.csv("min_pond_area_outflow_25.tsv", sep='\t', header=TRUE)
min_pa_o_25 <- min_pond_area_o_25$Outflow...Final

# max pond area outflow
max_pond_area_o_25 <- read.csv("max_pond_area_outflow_25.tsv", sep='\t', header=TRUE)
max_pa_o_25 <- max_pond_area_o_25$Outflow...Final

# min weir angle outflow
min_weir_angle_o_25 <- read.csv("min_weir_angle_outflow_25.tsv", sep='\t', header=TRUE)
min_wa_o_25 <- min_weir_angle_o_25$Outflow...Final

# max weir angle outflow
max_weir_angle_o_25 <- read.csv("max_weir_angle_outflow_25.tsv", sep='\t', header=TRUE)
max_wa_o_25 <- max_weir_angle_o_25$Outflow...Final

# min pond area min weir angle outflow
min_pond_area_min_weir_angle_o_25 <- read.csv("min_area_angle_outflow_25.tsv", sep='\t', header=TRUE)
min_pa_min_wa_o_25 <- min_pond_area_min_weir_angle_o_25$Outflow...Final

# min pond area max weir angle outflow
min_pond_area_max_weir_angle_o_25 <- read.csv("min_area_max_angle_outflow_25.tsv", sep='\t', header=TRUE)
min_pa_max_wa_o_25 <- min_pond_area_max_weir_angle_o_25$Outflow...Final

# max pond area min weir angle outflow
max_pond_area_min_weir_angle_o_25 <- read.csv("max_area_min_angle_outflow_25.tsv", sep='\t', header=TRUE)
max_pa_min_wa_o_25 <- max_pond_area_min_weir_angle_o_25$Outflow...Final

# max pond area max weir angle outflow
max_pond_area_max_weir_angle_o_25 <- read.csv("max_area_angle_outflow_25.tsv", sep='\t', header=TRUE)
max_pa_max_wa_o_25 <- max_pond_area_max_weir_angle_o_25$Outflow...Final

```

25% Impervious Plots
```{r }

plot(time,base_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, min_pa_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, max_pa_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, min_wa_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, max_wa_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, max_pa_max_wa_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, max_pa_min_wa_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, min_pa_min_wa_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, min_pa_max_wa_25, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

```
25% Impervious Inflow/Outflow Plots
```{r }
plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, base_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_wa_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_wa_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_min_wa_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_max_wa_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_min_wa_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_25, type="l", col="magenta", lwd=4, xlab="", ylab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_max_wa_o_25, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)
```
Reading Water Level Files 10% impervious:
```{r}
# base water level
basecase_10 <- read.csv("base_WL_10.tsv", sep='\t', header=TRUE)
base_10 <- basecase_10$Pond.Water.Level...Final
time_10 <- basecase_10$Time..Hour.

#min pond area
min_pond_area_10 <- read.csv("min_pond_area_10.tsv", sep='\t', header=TRUE)
min_pa_10 <- min_pond_area_10$Pond.Water.Level...Final

#max pond area
max_pond_area_10 <- read.csv("max_area_10.tsv", sep='\t', header=TRUE)
max_pa_10 <- max_pond_area_10$Pond.Water.Level...Final

#min weir angle
min_weir_angle_10 <- read.csv("min_weir_angle_10.tsv", sep='\t', header=TRUE)
min_wa_10 <- min_weir_angle_10$Pond.Water.Level...Final

#max weir angle
max_weir_angle_10 <- read.csv("max_weir_angle_10.tsv", sep='\t', header=TRUE)
max_wa_10 <- max_weir_angle_10$Pond.Water.Level...Final

# min pond area min weir angle
min_pond_area_min_weir_angle_10 <- read.csv("min_area_angle_10.tsv", sep='\t', header=TRUE)
min_pa_min_wa_10 <- min_pond_area_min_weir_angle_10$Pond.Water.Level...Final

# min pond area max weir angle 
min_pond_area_max_weir_angle_10 <- read.csv("min_area_max_angle_10.tsv", sep='\t', header=TRUE)
min_pa_max_wa_10 <- min_pond_area_max_weir_angle_10$Pond.Water.Level...Final

# max pond area min weir angle 
max_pond_area_min_weir_angle_10 <- read.csv("max_area_min_angle_10.tsv", sep='\t', header=TRUE)
max_pa_min_wa_10 <- max_pond_area_min_weir_angle_10$Pond.Water.Level...Final

# max pond area max weir angle 
max_pond_area_max_weir_angle_10 <- read.csv("max_area_angle_10.tsv", sep='\t', header=TRUE)
max_pa_max_wa_10 <- max_pond_area_max_weir_angle_10$Pond.Water.Level...Final

```

Reading Inflow/Outflow Files 10% impervious:
```{r}
# base inflow
basecase_i_10 <- read.csv("base_inflow_10.tsv", sep='\t', header=TRUE)
time_hydrograph <- basecase_i_10$Time..Hour.
base_i_10 <- basecase_i_10$Total.Inflow...Final

# base outflow
basecase_o_10 <- read.csv("base_outflow_10.tsv", sep='\t', header=TRUE)
base_o_10 <- basecase_o_10$Outflow...Final

# min pond area outflow
min_pond_area_o_10 <- read.csv("min_pond_area_outflow_10.tsv", sep='\t', header=TRUE)
min_pa_o_10 <- min_pond_area_o_10$Outflow...Final

# max pond area outflow
max_pond_area_o_10 <- read.csv("max_area_outflow_10.tsv", sep='\t', header=TRUE)
max_pa_o_10 <- max_pond_area_o_10$Outflow...Final

# min weir angle outflow
min_weir_angle_o_10 <- read.csv("min_weir_angle_outflow_10.tsv", sep='\t', header=TRUE)
min_wa_o_10 <- min_weir_angle_o_10$Outflow...Final

# max weir angle outflow
max_weir_angle_o_10 <- read.csv("max_weir_angle_outflow_10.tsv", sep='\t', header=TRUE)
max_wa_o_10 <- max_weir_angle_o_10$Outflow...Final

# min pond area min weir angle outflow
min_pond_area_min_weir_angle_o_10 <- read.csv("min_area_angle_outflow_10.tsv", sep='\t', header=TRUE)
min_pa_min_wa_o_10 <- min_pond_area_min_weir_angle_o_10$Outflow...Final

# min pond area max weir angle outflow
min_pond_area_max_weir_angle_o_10 <- read.csv("min_area_max_angle_outflow_10.tsv", sep='\t', header=TRUE)
min_pa_max_wa_o_10 <- min_pond_area_max_weir_angle_o_10$Outflow...Final

# max pond area min weir angle outflow
max_pond_area_min_weir_angle_o_10 <- read.csv("max_area_min_angle_outflow_10.tsv", sep='\t', header=TRUE)
max_pa_min_wa_o_10 <- max_pond_area_min_weir_angle_o_10$Outflow...Final

# max pond area max weir angle outflow
max_pond_area_max_weir_angle_o_10 <- read.csv("max_area_angle_outflow_10.tsv", sep='\t', header=TRUE)
max_pa_max_wa_o_10 <- max_pond_area_max_weir_angle_o_10$Outflow...Final

```

10% Impervious Plots
```{r }

plot(time,base_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, min_pa_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, max_pa_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, min_wa_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, max_wa_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, max_pa_max_wa_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, max_pa_min_wa_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, min_pa_min_wa_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)

plot(time, min_pa_max_wa_10, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "", ylab="", yaxt="n", xaxt="n")
title(ylab="Water Level (m)", line=1, cex.lab=2.5)
title(xlab="Time (hr)", line=1, cex.lab=2.5)


```
10% Impervious Inflow/Outflow Plots
```{r }
plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", lab=c(length(w),5,7), xaxt="n")
lines(time_hydrograph, base_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)


plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_wa_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_wa_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_min_wa_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_max_wa_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_min_wa_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

plot(time_hydrograph, base_i_10, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_max_wa_o_10, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0.6, cex.lab=3)
title(xlab="Time (hr)", line=1.3, cex.lab=3)

```

Reading Water Level Files 50% impervious:
```{r}
# base water level
basecase_50 <- read.csv("base_WL_50.tsv", sep='\t', header=TRUE)
base_50 <- basecase_50$Pond.Water.Level...Final
time_50 <- basecase_50$Time..Hour.

#min pond area
min_pond_area_50 <- read.csv("min_pond_area_50.tsv", sep='\t', header=TRUE)
min_pa_50 <- min_pond_area_50$Pond.Water.Level...Final

#max pond area
max_pond_area_50 <- read.csv("max_pond_area_50.tsv", sep='\t', header=TRUE)
max_pa_50 <- max_pond_area_50$Pond.Water.Level...Final

#min weir angle
min_weir_angle_50 <- read.csv("min_weir_angle_50.tsv", sep='\t', header=TRUE)
min_wa_50 <- min_weir_angle_50$Pond.Water.Level...Final

#max weir angle
max_weir_angle_50 <- read.csv("max_weir_angle_50.tsv", sep='\t', header=TRUE)
max_wa_50 <- max_weir_angle_50$Pond.Water.Level...Final

# min pond area min weir angle
min_pond_area_min_weir_angle_50 <- read.csv("min_area_angle_50.tsv", sep='\t', header=TRUE)
min_pa_min_wa_50 <- min_pond_area_min_weir_angle_50$Pond.Water.Level...Final

# min pond area max weir angle 
min_pond_area_max_weir_angle_50 <- read.csv("min_area_max_angle_50.tsv", sep='\t', header=TRUE)
min_pa_max_wa_50 <- min_pond_area_max_weir_angle_50$Pond.Water.Level...Final

# max pond area min weir angle 
max_pond_area_min_weir_angle_50 <- read.csv("max_area_min_angle_50.tsv", sep='\t', header=TRUE)
max_pa_min_wa_50 <- max_pond_area_min_weir_angle_50$Pond.Water.Level...Final

# max pond area max weir angle 
max_pond_area_max_weir_angle_50 <- read.csv("max_area_angle_50.tsv", sep='\t', header=TRUE)
max_pa_max_wa_50 <- max_pond_area_max_weir_angle_50$Pond.Water.Level...Final

```

Reading Inflow/Outflow Files 50% impervious:
```{r}
# base inflow
basecase_i_50 <- read.csv("base_inflow_50.tsv", sep='\t', header=TRUE)
time_hydrograph <- basecase_i_50$Time..Hour.
base_i_50 <- basecase_i_50$Total.Inflow...Final

# base outflow
basecase_o_50 <- read.csv("base_outflow_50.tsv", sep='\t', header=TRUE)
base_o_50 <- basecase_o_50$Outflow...Final

# min pond area outflow
min_pond_area_o_50 <- read.csv("min_pond_area_outflow_50.tsv", sep='\t', header=TRUE)
min_pa_o_50 <- min_pond_area_o_50$Outflow...Final

# max pond area outflow
max_pond_area_o_50 <- read.csv("max_pond_area_outflow_50.tsv", sep='\t', header=TRUE)
max_pa_o_50 <- max_pond_area_o_50$Outflow...Final

# min weir angle outflow
min_weir_angle_o_50 <- read.csv("min_weir_angle_outflow_50.tsv", sep='\t', header=TRUE)
min_wa_o_50 <- min_weir_angle_o_50$Outflow...Final

# max weir angle outflow
max_weir_angle_o_50 <- read.csv("max_weir_angle_outflow_50.tsv", sep='\t', header=TRUE)
max_wa_o_50 <- max_weir_angle_o_50$Outflow...Final

# min pond area min weir angle outflow
min_pond_area_min_weir_angle_o_50 <- read.csv("min_area_angle_outflow_50.tsv", sep='\t', header=TRUE)
min_pa_min_wa_o_50 <- min_pond_area_min_weir_angle_o_50$Outflow...Final

# min pond area max weir angle outflow
min_pond_area_max_weir_angle_o_50 <- read.csv("min_area_max_angle_outflow_50.tsv", sep='\t', header=TRUE)
min_pa_max_wa_o_50 <- min_pond_area_max_weir_angle_o_50$Outflow...Final

# max pond area min weir angle outflow
max_pond_area_min_weir_angle_o_50 <- read.csv("max_area_min_angle_outflow_50.tsv", sep='\t', header=TRUE)
max_pa_min_wa_o_50 <- max_pond_area_min_weir_angle_o_50$Outflow...Final

# max pond area max weir angle outflow
max_pond_area_max_weir_angle_o_50 <- read.csv("max_area_angle_outflow_50.tsv", sep='\t', header=TRUE)
max_pa_max_wa_o_50 <- max_pond_area_max_weir_angle_o_50$Outflow...Final

```

50% Impervious Plots
```{r }

plot(time,base_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")
plot(time, min_pa_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")
plot(time, max_pa_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")
plot(time, min_wa_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")
plot(time, max_wa_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")
plot(time, max_pa_max_wa_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")
plot(time, max_pa_min_wa_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")
plot(time, min_pa_min_wa_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")
plot(time, min_pa_max_wa_50, type="l", col="blue", lwd=2, ylim=c(min(base_25),max(min_pa_min_wa_25)), xlab= "Time (hours)", ylab="Water Level (m)")

```

50% Impervious Inflow/Outflow Plots
```{r }
plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", lab=c(length(w),5,7), xaxt="n")
lines(time_hydrograph, base_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)


plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)

plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)

plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_wa_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)

plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_wa_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)

plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_min_wa_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)

plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, min_pa_max_wa_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)

plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_min_wa_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)

plot(time_hydrograph, base_i_50, type="l", col="magenta", lwd=4, ylab="", xlab="", yaxt="n", xaxt="n")
lines(time_hydrograph, max_pa_max_wa_o_50, col="chartreuse3", lwd=4)
title(ylab="Flow (m3/hr)", line=0, cex.lab=1.2)
title(xlab="Time (hr)", line=0, cex.lab=1.2)

```

